`r params$project_title`

### 2021-06-17 reports/rmarkdown/02_individual_reports.Rmd
update

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  dataset: 1
---

```{r Setup, echo = FALSE}
knitr::opts_chunk$set(fig.width  = 10,
                      results    = "hold",
                      message    = FALSE,
                      warning    = FALSE)
```

@@

```{r, echo = FALSE}
PATH <- "~/Desktop/NBIS/SMS_Projects/broliden_5325" #Path to the data
PATH <- "../.." #Path to the data

@@

```{r, echo = FALSE}
# Load metadata
metadata <- read.csv(paste0(PATH,"/data/Clinical_visit_2_3_updatesept28.csv"))
rownames(metadata) <- as.character(metadata$ID)

>>>>

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  dataset: 2
---

```{r Setup, echo = FALSE}
knitr::opts_chunk$set(fig.width  = 10,
                      results    = "hold",
                      message    = FALSE,
                      warning    = FALSE)
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown")
```

@@

```{r, echo = FALSE}
PATH <- "../../" #Path to the data

@@

```{r, echo = FALSE}
# Load metadata
metadata <- read.csv(paste0(PATH,"data/Clinical_visit_2_3_updatefeb22.csv"))
rownames(metadata) <- as.character(metadata$ID)
